
\keywords{%
  безопасность данных,
  интеллектуальные системы,
  облачные вычисления,
  общественная Wi-Fi сеть,
  целевая реклама
}

\abstractcontent{
Данная работа посвящена разработке системы формирования рекламных сообщений. В качестве исходных данных система использует данные, указанные клиентами при регистрации в открытой Wi-Fi сети. Для выполнения задачи формирования рекламных сообщений используется информация о местах, посещенных зарегистрированными клиентами. Эту информацию позволяют собирать специально созданные Wi-Fi сканеры. В работе рассмотрена структура интеллектуальных систем, как способ организации генератора рекламных сообщений. Рассмотрено и обосновано применение облачных технологий в качестве платформы для анализа данных. Разработана и реализована структура системы и каждого ее компонента. Проведено тестирование полученной системы.
}

\keywordsen{
  cloud computing,
  data security,
  intelligent systems,
  public Wi-Fi network,
  targeted advertising,
}

\abstractcontenten{
This work is devoted to the development of the system for the formation of advertising messages. As the initial data, the system uses the data specified by the clients when registering in an open Wi-Fi network. To perform the task of forming advertising messages, information about the places visited by registered customers is used. This information allows you to collect specially created Wi-Fi scanners. In this paper, the structure of intelligent systems is considered as a way to organize an advertising message generator. The application of cloud technologies as a platform for data analysis is considered and justified. The structure of the system and each of its components has been developed and implemented. The system was tested.
}
